Ground state energy of quantum dots using the coupled cluster method

### 2018-05-09 project_2/article/article.tex
Start on section on RHF

            Starting from the bottom and working our way upwards from left to
            right we can label each line from $0$ to $n$ in increasing
            order. This enumeration will serve as our common quantum number
            $\alpha$\footnote{Note that we use greek letters $\alpha, \beta,
            \dots$ for the harmonic oscillator wavefunctions as opposed to latin
            letters for the general indices.}.

            The normalization condition now reads
            \begin{align}
                \braket{\alpha}{\beta}
                = \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta},
            \end{align}
            The one-body matrix will now be a diagonal matrix with the
            eigenenergies of single particle harmonic oscillator functions as
            elements.
            \begin{align}
                \bra{\alpha}h\ket{\beta}
                = \epsilon_{\beta}
                \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta}.
            \end{align}

            The two-body matrix elements are a little harder to work out as the
            harmonic oscillator wavefunctions are not eigenfunctions to the
            correlation operator. Luckily, from E. Anisimovas and A.
            Matulis\cite{anisimovas1998energy} we can get an analytical
            expression for the two-body matrix elements.

>>>>

            Starting from the bottom and working our way upwards from left to
            right we can label each line from $0$ to $n$ in increasing
            order. This enumeration will serve as our common quantum number
            $\alpha$\footnote{Note that we use greek letters $\alpha, \beta,
            \dots$ for the harmonic oscillator wavefunctions as opposed to latin
            letters for the general indices.}. We will only work with full
            \emph{shells}, i.e., we restrict our views to systems of $N$
            particles where $N$ will be a magic number which we get by counting
            all spin states for each energy level and the energy levels below.
            In \autoref{fig:basis_states} we can see the magic number $N \in [2,
            6, 12]$.

            The normalization condition now reads
            \begin{align}
                \braket{\alpha}{\beta}
                = \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta},
            \end{align}
            The one-body matrix will be a diagonal matrix with the eigenenergies
            of the single particle harmonic oscillator functions as elements.
            \begin{align}
                \bra{\alpha}h\ket{\beta}
                = \epsilon_{\beta}
                \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta}.
            \end{align}

            The two-body matrix elements are a little harder to work out as the
            harmonic oscillator wavefunctions are not eigenfunctions to the
            correlation operator. Luckily, from E. Anisimovas and A.  Matulis
            (Equation A2)\cite{anisimovas1998energy} we can get an analytical
            expression for the two-body matrix elements. We can then construct
            the antisymmetric two-body matrix elements in the harmonic
            oscillator basis.
            \begin{align}
                \bra{\alpha\beta}\ket{\gamma\delta}
                &= \braket{\alpha\beta}{\gamma\delta}
                - \braket{\alpha\beta}{\delta\gamma}.
            \end{align}
            As we only need to compute these once it is a good idea to save all
            non-zero values of $\bra{\alpha\beta}\ket{\gamma\delta}$ to a file.

        \subsubsection{Constructing the Hartree-Fock basis}
            Having found the matrix elements of $h$ and $u$ we can now use the
            \emph{self-consistent field iteration} method to construct $h$ and
            $u$ in a \emph{restricted Hartree-Fock} basis. This will yield a
            better estimate to the actual, unknown basis functions of the
            system.
